Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-06-19 paper.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Generally, embedded computer systems perform dedicated functions with a high degree of reliability, according to their original design and requirements ({\it e.g.}, real time). They are ubiquitous in modern day information systems and are also becoming increasingly important in our society, due to their use to process, monitor, control, and even replace every human activity: factories, power plants, mobile devices, robotics, traffic control, vehicles, and home appliances. Besides, they are also used in a variety of sophisticated applications, which range from entertainment software, such as games and graphics animation, to safety-critical systems, such as nuclear reactors and automotive controllers~\cite{Kopetz11}.

>>>>

Generally, embedded computer systems perform dedicated functions with a high degree of reliability, according to their original design and requirements ({\it e.g.}, real-time). They are ubiquitous in modern day information systems and are also becoming increasingly important in our society, due to their use to process, monitor, control, and even replace every human activity: factories, power plants, mobile devices, robotics, traffic control, vehicles, and home appliances. Besides, they are also used in a variety of sophisticated applications, which range from entertainment software, such as games and graphics animation, to safety-critical systems, such as nuclear reactors and automotive controllers~\cite{Kopetz11}.
